Expectations bias moral evaluations

### 2018-09-06 paper/paper-apa.Rmd
added reg table

library(tidyverse)

@@

```{r fit brms models, include=FALSE}
library(brms)
devtools::source_gist(id = "f1994c0f8325abbc5d300600744af39d", filename="cbrm.R")

@@

coefs_exp1 <- broom::tidy(fit_exp1rand) %>%
  filter(term=="b_intercept")

@@

```{r}
my_citations <- cite_r(
  file = "r-references.bib"
  , pkgs = c("tidyverse", "brms", "gridExtra", "papaja")
  , withhold = FALSE
  # , footnote = TRUE
)
```

@@

We predicted that participants would evaluate unexpected events as more upsetting than expected events. We estimated the magnitude of this effect by fitting a cumulative (ordinal) random effects model with participants’ scale responses as the dependent variable (1 to 5) and random intercepts for item and subject. This model produces four intercept coefficients, representing the cumulative log-odds of responses at each scale point or lower. For instance, the second coefficient represents the log-odds participants chose a 2 ("outcome 2 seems slightly more upsetting") or lower on the scale. Similarly, the third intercept coefficient represents the log-odds participants chose a 3 or lower on the scale. To examine the predicted effect, we compared the third intercept coefficient (representing the log-odds of choosing 4 or higher) to the inverse of the second intercept coefficient (thereby representing the log-odds *not* choosing a 3 or higher--i.e., choosing a 1 or 2), allowing us to test whether participants were more likely to choose the expected or unexpected event as being more upsetting in cases where they did not choose the neither option. This analysis indicated that people were more likely to think that events that were unexpected were more upsetting than events that were expected, $BF_{01}$ `r print_bf(bf_exp2)` (see supporting information for full model results). We observed this difference consistently across nearly every item (Figure 2).

@@

>>>>

library(tidyverse)
library(broom)
library(brms)

@@

```{r fit brms models, include=FALSE}

devtools::source_gist(id = "f1994c0f8325abbc5d300600744af39d", filename="cbrm.R")

@@

coefs_exp1 <- tidy(fit_exp1rand) %>%
  filter(term=="b_intercept")

@@

```{r}
my_citations <- cite_r(
  file = "r-references.bib"
  , pkgs = c("tidyverse", "brms", "broom", "gridExtra", "papaja")
  , withhold = FALSE
  # , footnote = TRUE
)
```

@@

We predicted that participants would evaluate unexpected events as more upsetting than expected events. We estimated the magnitude of this effect by fitting a cumulative (ordinal) random effects model with participants’ scale responses as the dependent variable (1 to 5) and random intercepts for item and subject. This model produces four intercept coefficients, representing the cumulative log-odds of responses at each scale point or lower (summarized in Table 1). For instance, the second coefficient represents the log-odds participants chose a 2 ("outcome 2 seems slightly more upsetting") or lower on the scale. Similarly, the third intercept coefficient represents the log-odds participants chose a 3 or lower on the scale. To examine the predicted effect, we compared the third intercept coefficient (representing the log-odds of choosing 4 or higher) to the inverse of the second intercept coefficient (thereby representing the log-odds *not* choosing a 3 or higher--i.e., choosing a 1 or 2), allowing us to test whether participants were more likely to choose the expected or unexpected event as being more upsetting in cases where they did not choose the neither option. This analysis indicated that people were more likely to think that events that were unexpected were more upsetting than events that were expected, $BF_{01}$ `r print_bf(bf_exp2)`. We observed this difference consistently across nearly every item (Figure 2).

@@

```{r, results="asis"}
tidy(fit_exp2rand) %>%
  filter(grepl("b_Intercept", term), !grepl("prior", term)) %>%
  mutate(
    Term = gsub("b_","",term),
    `95\\% conf. interval` = paste0("[",round(lower,3), ", ", round(upper,3), "]"),
    B = estimate,
    `SE B` = std.error,
    `$e^B$` = exp(B)
    ) %>%
  select(Term, B, `SE B`, `95\\% conf. interval`) %>%
  apa_table(caption="Bayesian regression results for Experiment 2.", 
            escape=FALSE,
            align = c("r","c","c","c"))
```
